Model-based variable selection for regression with highly correlated variables.

### 2014-06-11 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@638 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}[h!]
	\begin{minipage}[l]{.30\linewidth}
			\includegraphics[width=150px]{figures/correlbeforeafter.png} 
			\caption{Correlations between the covariates in $\boldsymbol{X}$ (upper) and $\hat{\boldsymbol{X}}_f$ (lower).}
	\end{minipage} \hfill
	\begin{minipage}[c]{.30\linewidth}
				\includegraphics[height=150px,width=150px]{figures/histcorrelBVBI.png} 
			\caption{Histogram of correlations in $\boldsymbol{X}$.} 
	\end{minipage} \hfill
   \begin{minipage}[r]{.30\linewidth}
			\includegraphics[height=150px, width=150px]{figures/R2corregBVBI.png} 
			\caption{$R^2_{adj}$ of the 55 sub-regressions.}\label{R2bv}
   \end{minipage}
\end{figure}   	
CorReg found 55 sub-regressions as shown in Figure \ref{R2bv}. One of them seems to be weak $R^2=0.17$ but is not linear (points out a link between diameter of a coil and some shape indicator).

The response variable was binary but $n$ was too small compared to $p$ to use logistic regression so we have considered $\boldsymbol{Y}$ as a continuous variable and then made imputation by $1$ when $\hat{\boldsymbol{Y}}>0.5$ and by $0$ else.

>>>>

		\begin{figure}[h!]
	\begin{minipage}[t]{.30\linewidth}
			\includegraphics[height=150px,width=150px]{figures/nbcompBV.png}%{figures/mixmod.png} 
			\caption{Distribution of the number of components found for each covariate.}\label{graphMixmod}
	\end{minipage} \hfill
	\begin{minipage}[t]{.30\linewidth}
			\includegraphics[height=150px, width=150px]{figures/GMcriseBV.png}%{figures/histR2exfos.png} $R^2_{adj}$ of the 76 sub-regressions.
			\caption{Another example of non-Gaussian real variable easily modeled by a Gaussian mixture.}
	\end{minipage} \hfill
   \begin{minipage}[t]{.30\linewidth}
			\includegraphics[height=150px,width=150px]{figures/histcorrelBVBI.png} 
			\caption{Histogram of correlations in $\boldsymbol{X}$.} \label{compareMSEexfos}
   \end{minipage}
\end{figure}

CorReg found 55 sub-regressions as shown in Figure \ref{R2bv}. One of them seems to be weak $R^2=0.17$ but is not linear (points out a link between diameter of a coil and some shape indicator).

\begin{figure}
\centering
	\includegraphics[height=150px, width=150px]{figures/R2corregBVBI.png} 
			\caption{$R^2_{adj}$ of the 55 sub-regressions.}\label{R2bv}
\end{figure}
The response variable was binary but $n$ was too small compared to $p$ to use logistic regression so we have considered $\boldsymbol{Y}$ as a continuous variable and then made imputation by $1$ when $\hat{\boldsymbol{Y}}>0.5$ and by $0$ else.
